COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries: Replication Code

### 2021-07-02 2_tables.Rmd
cleaning of code

```{r setup3, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

@@

lm_helper <- function(data,...) {
  data %>% 
    study_weighting() %>% 
    estimatr::lm_robust(data = .,...) %>% 
    {bind_cols( tidy(.), n = nobs(.) )}
}

@@

loo_helper <- 
  function(data, 
           sample_var, 
           loo_n = 1,
           loo_fun = 
             function(dat) 
               lm_helper(data = dat, 
                         formula = take_vaccine_num ~ 1, 
                         cluster = cluster,
                         weight = weight, 
                         se_type = "stata")
  ) {

@@

# Illustration of loo_helper
# loo_helper(
#   data = data.frame(country = 1:3, Y = 1:3),
#   loo_n = 2,
#   sample_var = "country",
#   loo_fun = function(dat) mean(dat$Y) 
# )

@@

grp_analysis <- function(df, y, x)

  df %>%
    dplyr::filter(if_all(c(all_of(x), all_of(y), cluster, weight), ~ !is.na(.))) %>%
    dplyr::nest_by(group, get(x)) %>%
    dplyr::summarize(
      lm_helper(data = data, 
                formula = as.formula(paste0(y, "~ 1")), cluster = cluster,
                weight = weight, se_type = "stata"), .groups = "drop") %>% 
    dplyr::rename(!!x := "get(x)")

@@

reasons_together <- function(df, reason, num = "Yes")

  df %>%
    dplyr::filter(take_vaccine %in% num, 
                  if_all(c(all_of(reason), cluster, weight), ~ !is.na(.))) %>%
    dplyr::nest_by(group) %>%
    dplyr::summarize(
      lm_helper(data = data, 
                formula = as.formula(paste0(reason, "~ 1")), 
                cluster = cluster,
                weight = weight, se_type = "stata"), .groups = "drop")

reasons_together_subgroup <- function(df, reason, num = "Yes", 
                                      dem_group = NA, dem_subgroup = NA){

@@

age_analysis <- function(df, reason, num = "Yes", filter_by=NA){
  df %>%
    dplyr::filter({{filter_by}}==1)  %>%
    dplyr::filter(take_vaccine %in% num, 
                  if_all(c(all_of(reason), cluster, weight), ~ !is.na(.))) %>%
    dplyr::nest_by(group) %>%
    dplyr::summarize(
      lm_helper(data = data, 
                formula = as.formula(paste0(reason, "~ 1")), 
                cluster = cluster,
                weight = weight, se_type = "stata"), .groups = "drop")
}

@@

nas <- df %>% group_by(country) %>%
  summarize(n = n(),
            take_vaccine_na = mean(!is.na(take_vaccine))*100,
            gender_na = mean(!is.na(gender))*100,
            educ_na= mean(!is.na(educ))*100,
            age_na= mean(!is.na(age))*100) %>%
  kable(digits = 2, 
        col.names= c("Country", "N obs", "Take vaccine", "Gender", "Education", "Age"),
        caption = "Observations and missingness patterns", 
        booktabs = TRUE, linesep = "", 
        format.args = list(big.mark = ",", scientific = FALSE),
  format = "latex") %>% 
  kableExtra::kable_styling(font_size = base_font_size - 2, full_width = FALSE) %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table S8 show the proportion of observations that are not missing values for each variable included in Figure 1.",
    threeparttable = T)

df %>% group_by(country) %>%
  summarize(n = n(),
            take_vaccine_na = mean(!is.na(take_vaccine)) *100,
            gender_na = mean(is.na(gender))*100,
            educ_na= mean(is.na(educ))*100,
            age_na= mean(is.na(age))*100) %>%
  kable(digits = 2, 
        col.names= c("Country", "N obs", "Take vaccine", "Gender", "Education", "Age"),
        caption = "Observations and missingness patterns.", 
        linesep = "", 
        format.args = list(big.mark = ",", scientific = FALSE),
  format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table S8 show the percentage of observations that are not missing values for each variable included in Figure 1.",
    threeparttable = T)

@@

tab_sampling <- 
  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select("Study" = "country", "Date"="date",
                "Geographic scope", "Sampling methodology", "Survey modality", "Weights") %>%
  knitr::kable(
    caption =  "Summary of studies sampling",
    format = "latex", booktabs = T, linesep = "", label = "sampling") %>% 
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
                            font_size = base_font_size - 2) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1:2, width = "8em") %>%
  kableExtra::column_spec(3, width = "12em")  %>%
  kableExtra::column_spec(4, width = "30em") %>% 
  kableExtra::landscape()

readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select("Study" = "country", "Date"="date",
                "Geographic scope", "Sampling methodology", "Survey modality", "Weights") %>%
  knitr::kable(caption =  "Summary of studies' sampling", linesep = "", format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1:2, width = "8em") %>%
  kableExtra::column_spec(3, width = "12em")  %>%
  kableExtra::column_spec(4, width = "30em") %>% 
  kableExtra::landscape()
```

@@

# Age (all original categories and binary recoding)
acc_by_age <- grp_analysis(df2, y = "take_vaccine_num", x = "age_groups_three") %>%
  dplyr::filter(statistic!=Inf) %>%
  dplyr::filter(conf.low>0)
acc_by_age_binary <- grp_analysis(df2, y = "take_vaccine_num", x = "age_groups_binary")

@@

nationals <- df2 %>%
  filter(country=="Burkina Faso" |
           country=="Colombia" |
           country=="Rwanda" |
           country=="Sierra Leone 1" |
           country=="Sierra Leone 2")

@@

# Age (all original categories and binary recoding)
acc_by_age_n <- grp_analysis(nationals, y = "take_vaccine_num", x = "age_groups_three") %>%
  dplyr::filter(statistic!=Inf) %>%
  dplyr::filter(conf.low>0)

ans_n <- 
  dplyr::bind_rows(
    main_results_n %>% mutate(cat = "All", var = "All"),
    acc_by_gender_n %>% rename(cat = gender) %>% mutate(var = "By gender"),
    acc_by_educ_binary_n %>% rename(cat = educ_binary) %>% mutate(var = "By education"),
    acc_by_age_n %>% rename(cat = age_groups_three) %>% mutate(var = "By age")) %>%
  dplyr::mutate(across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 1))) %>%
  filter(group=="All") %>%
  mutate(group="All LMICs (National samples)",
         tag="All LMICs (National samples)")

@@

ans_national <- ans_n %>% filter(group == "All LMICs (National samples)" & cat=="All")

@@

fig_hist_loo <- 
  loo_estimates %>%
  dplyr::mutate(estimate = estimate*100) %>% 
  ggplot(aes(estimate, color = tag, fill = tag)) + 
  geom_histogram(aes(y = ..density..), bins = 200, 
                 position = "dodge", alpha = .3, size = .3) +
  geom_vline(data = ans_loo, 
             aes(xintercept = estimate, color = cat, linetype = group), size = .9) +
  facet_grid_paginate(var + tag ~ m)  +
  scale_color_manual(
    name = "Subgroups", 
    values = safe_colorblind_palette) + 
  scale_fill_manual(
    name = "Subgroups", 
    values = safe_colorblind_palette) + 
  scale_linetype_manual(
    name = "Sample Average", 
    values = c("solid", "11", "dashed")) + 
  scale_x_continuous(n.breaks = 8, name = "estimate") +
  scale_y_continuous(labels = scales::percent_format(scale = 1, suffix = "", accuracy = 0.1)) +
  labs(title = "",
       x = "") +
  guides(color = guide_legend(reverse = TRUE, nrow = 2, keyheight = 1),
         fill = guide_legend(reverse = TRUE, nrow = 2, keyheight = 1),
         linetype = guide_legend(keyheight = 2)) +
  theme_bw(base_size = (base_font_size - 2)) +
  theme(legend.position = "bottom")

fig_hist_loo
```

@@

all_tables_n <- 
  main_table_n %>% 
  dplyr::left_join(gender_table_n) %>%
  dplyr::left_join(educ_table_n) %>% 
  dplyr::left_join(age_table_n) %>%
  dplyr::filter(group=="All") %>%
  dplyr::mutate(group="All LMICs (National)")

@@

#Table to Latex
tab_reasons_y <- 
  yes_vacc2 %>%
  knitr::kable(col.names = cnames,
      caption = "Reasons to take the vaccine", format = "latex", booktabs = T, 
      linesep = "", label = "yes", 
      format.args = list(big.mark = ",", scientific = FALSE), 
      escape = F, align = "lcccc") %>%
  kableExtra::kable_styling(full_width = FALSE, 
                            font_size = base_font_size - 2) %>%
  kableExtra::add_header_above(c(" " = 2, "Protection" = 3), bold = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>% 
  kableExtra::column_spec(2:4, width = "4em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table S2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine. The number of observations and percentage corresponds only to people who would take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses. Studies India, Pakistan 1 and Pakistan 2 are not included because they either did not include the question or were not properly harmonized with the other studies.",
    threeparttable = T)

yes_vacc2 %>%
  knitr::kable(col.names = cnames,
      caption = "\\label{yes}Reasons to take the vaccine", 
      booktabs = T, linesep = "", 
      format.args = list(big.mark = ",", scientific = FALSE)) %>% 
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::add_header_above(c(" " = 2, "Protection" = 3), bold = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>% 
  kableExtra::column_spec(2:5, width = "8em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table S2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine. The number of observations and percentage correponds only to people who would take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses. Studies India, Pakistan 1 and Pakistan 2 are not included because they either did not include the question or were not properly harmonized with the other studies.",
    threeparttable = T)

@@

## Generate data for analysis of yes reasons for different age groups
yes_vacc_age_1 <- 
  lapply(yes_vars, age_analysis, df = df2, num = "Yes", filter_by=`age_less24`) %>%
  dplyr::bind_rows() %>%
  mutate(age="<25")

yes_vacc_age_2 <- 
  lapply(yes_vars, age_analysis, df = df2, num = "Yes", filter_by=`age_25_54`) %>%
  dplyr::bind_rows() %>%
  mutate(age="25-54")

yes_vacc_age_3 <- 
  lapply(yes_vars, age_analysis, df = df2, num = "Yes", filter_by=`age_55_more`) %>%
  dplyr::bind_rows() %>%
  mutate(age="55+")

#Get percentage per yes reason category and make wide table
yes_vacc_age <- 
  rbind(yes_vacc_age_1, yes_vacc_age_2, yes_vacc_age_3) %>%
  dplyr::mutate(across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 0))) %>%
  dplyr::mutate(estimate = format(estimate, nsmall = 0),
                conf_int = paste0("(", conf.low, 
                                  ", ", conf.high, ")"),
                n=as.character(n)) %>%
  dplyr::select(group, estimate, conf_int, outcome, age, n) %>%
  tidyr::pivot_wider(names_from = c(outcome, age), values_from = c(estimate, conf_int, n), names_sep = "__") %>%
  tidyr::pivot_longer(cols = c(starts_with("estimate__"), starts_with("conf_int__"), starts_with("n__")),
                      names_to = c("type", ".value"),
                      names_pattern = "(.*)__(.*)")

y1 <- yes_vacc_age %>%
  dplyr::filter(grepl("yes_vaccine_1", type)) %>%
  mutate(type=ifelse(grepl("estimate", type), "estimate", type),
         type=ifelse(grepl("conf_int", type), "conf_int", type),
         type=ifelse(grepl("n__", type), "n", type))

y2 <- yes_vacc_age %>%
  dplyr::filter(grepl("yes_vaccine_2", type))%>%
  mutate(type=ifelse(grepl("estimate", type), "estimate", type),
         type=ifelse(grepl("conf_int", type), "conf_int", type),
         type=ifelse(grepl("n__", type), "n", type))

y3 <- yes_vacc_age %>%
  dplyr::filter(grepl("yes_vaccine_3", type))%>%
  mutate(type=ifelse(grepl("estimate", type), "estimate", type),
         type=ifelse(grepl("conf_int", type), "conf_int", type),
         type=ifelse(grepl("n__", type), "n", type))

yes_vacc_age <- left_join(y1, y2, by=c("group", "type")) %>%
  left_join(y3, by=c("group", "type")) %>% 
  dplyr::mutate(
    group = forcats::fct_relevel(as.factor(group), "All", "Russia", "USA", after = Inf)) %>% 
  dplyr::arrange(group) %>% 
  dplyr::mutate(across(c(group), ~ifelse(type == "conf_int", "Conf. interval", as.character(.))),
                across(c(group), ~ifelse(type == "n", "n", as.character(.))),
                group = ifelse(group == "All", "All LMICs", group)) %>% 
  dplyr::select(-type)

@@

#Table to Latex
tab_reasons_y_age <- 
  yes_vacc_age %>%
  knitr::kable(col.names = cnames,
      caption = "Reasons to take the vaccine- by age groups", format = "latex", booktabs = T, 
      linesep = "", label = "yes1", 
      format.args = list(big.mark = ",", scientific = FALSE), 
      escape = F, align = c("l", rep("c", 9))) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
                            font_size = base_font_size - 2, full_width = FALSE) %>%
  kableExtra::add_header_above(c(" " = 1, "Self" = 3, "Family" = 3, "Community" = 3), bold = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::row_spec(seq(from = 3, to = 36, by = 3), hline_after = TRUE) %>%
  kableExtra::column_spec(1, width = "7em") %>% 
  kableExtra::column_spec(2:10, width = "5em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table S4 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine by age groups. The number of observations and percentage correponds only to people who would take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses.",
    threeparttable = T)

yes_vacc_age %>%
  knitr::kable(col.names = cnames,
      caption = "\\label{yes1}Reasons to take the vaccine", 
      booktabs = T, linesep = "", 
      format.args = list(big.mark = ",", scientific = FALSE)) %>% 
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::add_header_above(c(" " = 1, "Self" = 3, "Family" = 3, "Community" = 3), bold = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>% 
  kableExtra::column_spec(2:10, width = "4em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table S4 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine by age groups. The number of observations and percentage correponds only to people who would take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses.",
    threeparttable = T)

@@

fig_2
```

@@

no_vacc2 %>%
  knitr::kable(
    col.names = c("Study", "N", 
                  "Concerned about side effects", 
                  "Concerned about getting coronavirus from the vaccine", 
                  "Not concerned about getting seriously ill", 
                  "Doesn't think vaccines are effective", 
                  "Doesn't think Coronavirus outbreak is as serious as people say", 
                  "Doesn't like needles", 
                  "Allergic to vaccines", 
                  "Won't have time to get vaccinated", 
                  "Mentions a conspiracy theory", 
                  "Other reasons"),
    caption = "\\label{no}Reasons not to take the vaccine", 
    booktabs = T, linesep = "", 
    format.args = list(big.mark = ",",scientific = FALSE)) %>%
  kableExtra::kable_styling(full_width = F) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1:12, width = "7em") %>%
  # kableExtra::column_spec(1, width = "7em") %>%
  kableExtra::footnote(
    general_title = "",
    general = "Table S5 shows percentage of respondents mentioning reasons why they would not take the Covid-19 vaccine. The number of observations and percentage correponds only to people who would NOT take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses.",
    threeparttable = T)
```

@@

trust <- filter(trust_vacc_together, sub=="Any")

@@

trust_all <- 
  trust %>% 
  dplyr::filter(group == "All" & tag=="Health workers") %>%
  dplyr::arrange(desc(estimate))

@@

fig_hist_categories
```

>>>>

```{r setup3, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

@@

lm_helper <- function(data,
                      ...) {
  data %>% 
    study_weighting() %>% 
    estimatr::lm_robust(data = .,...) %>% 
    {bind_cols( tidy(.), n = nobs(.) )}
}

@@

loo_helper <- function(data, 
                       sample_var, 
                       loo_n = 1,
                       loo_fun = 
                         function(dat) 
                           lm_helper(data = dat, 
                                     formula = take_vaccine_num ~ 1, 
                                     cluster = cluster,
                                     weight = weight, 
                                     se_type = "stata")) {

@@

# # Illustration of loo_helper
# loo_helper(
#   data = data.frame(country = 1:3, Y = 1:3),
#   loo_n = 2,
#   sample_var = "country",
#   loo_fun = function(dat) mean(dat$Y)
# )

@@

grp_analysis <- function(df, 
                         y, 
                         x) {
  df %>%
    dplyr::filter(if_all(c(all_of(x), all_of(y), cluster, weight), ~ !is.na(.))) %>%
    dplyr::nest_by(group, get(x)) %>%
    dplyr::summarize(
      lm_helper(data = data, 
                formula = as.formula(paste0(y, "~ 1")), cluster = cluster,
                weight = weight, se_type = "stata"), .groups = "drop") %>% 
    dplyr::rename(!!x := "get(x)")
}

@@

reasons_together <- function(df, 
                             reason, 
                             num = "Yes") {
  df %>%
    dplyr::filter(take_vaccine %in% num, 
                  if_all(c(all_of(reason), cluster, weight), ~ !is.na(.))) %>%
    dplyr::nest_by(group) %>%
    dplyr::summarize(
      lm_helper(data = data, 
                formula = as.formula(paste0(reason, "~ 1")), 
                cluster = cluster,
                weight = weight, se_type = "stata"), .groups = "drop")
}

reasons_together_subgroup <- function(df, 
                                      reason, num = "Yes", 
                                      dem_group = NA, 
                                      dem_subgroup = NA) {

@@

age_analysis <- function(df, 
                         reason, 
                         num = "Yes", 
                         filter_by = NA) {
  df %>%
    dplyr::filter({{filter_by}} == 1)  %>%
    dplyr::filter(take_vaccine %in% num, 
                  if_all(c(all_of(reason), cluster, weight), ~ !is.na(.))) %>%
    dplyr::nest_by(group) %>%
    dplyr::summarize(
      lm_helper(data = data, 
                formula = as.formula(paste0(reason, "~ 1")), 
                cluster = cluster,
                weight = weight, se_type = "stata"), .groups = "drop")
}

@@

nas <- df %>% group_by(country) %>%
  summarize(n = n(),
            take_vaccine_na = mean(!is.na(take_vaccine))*100,
            gender_na = mean(!is.na(gender))*100,
            educ_na = mean(!is.na(educ))*100,
            age_na = mean(!is.na(age))*100) %>%
  kable(digits = 2, 
        col.names = c("Country", "N obs", "Take vaccine", "Gender", "Education", "Age"),
        caption = "Observations and missingness patterns", 
        booktabs = TRUE, linesep = "", 
        format.args = list(big.mark = ",", scientific = FALSE),
  format = "latex") %>% 
  kableExtra::kable_styling(font_size = base_font_size - 2, full_width = FALSE) %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table S8 show the proportion of observations that are not missing values for each variable included in Figure 1.",
    threeparttable = T)

df %>% group_by(country) %>%
  summarize(n = n(),
            take_vaccine_na = mean(!is.na(take_vaccine)) * 100,
            gender_na = mean(is.na(gender)) * 100,
            educ_na = mean(is.na(educ)) * 100,
            age_na = mean(is.na(age)) * 100) %>%
  kable(digits = 2, 
        col.names = c("Country", "N obs", "Take vaccine", "Gender", "Education", "Age"),
        caption = "Observations and missingness patterns.", 
        linesep = "", 
        format.args = list(big.mark = ",", scientific = FALSE),
  format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table S8 show the percentage of observations that are not missing values for each variable included in Figure 1.",
    threeparttable = T)

@@

tab_sampling <- 
  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select("Study" = "country", "Date" = "date",
                "Geographic scope", "Sampling methodology", "Survey modality", "Weights") %>%
  knitr::kable(
    caption =  "Summary of studies sampling",
    format = "latex", booktabs = T, linesep = "", label = "sampling") %>% 
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
                            font_size = base_font_size - 2) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1:2, width = "8em") %>%
  kableExtra::column_spec(3, width = "12em")  %>%
  kableExtra::column_spec(4, width = "30em") %>% 
  kableExtra::landscape()

readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select("Study" = "country", "Date" = "date",
                "Geographic scope", "Sampling methodology", "Survey modality", "Weights") %>%
  knitr::kable(caption =  "Summary of studies' sampling", linesep = "", format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1:2, width = "8em") %>%
  kableExtra::column_spec(3, width = "12em")  %>%
  kableExtra::column_spec(4, width = "30em") %>% 
  kableExtra::landscape()
```

@@

# Age (all original categories and binary recoding)
acc_by_age <- 
  grp_analysis(df2, y = "take_vaccine_num", x = "age_groups_three") %>%
  dplyr::filter(statistic != Inf) %>%
  dplyr::filter(conf.low > 0)

acc_by_age_binary <- grp_analysis(df2, y = "take_vaccine_num", x = "age_groups_binary")

@@

nationals <- 
  df2 %>%
  dplyr::filter(country == "Burkina Faso" |
           country == "Colombia" |
           country == "Rwanda" |
           country == "Sierra Leone 1" |
           country == "Sierra Leone 2")

@@

# Age (all original categories and binary recoding)
acc_by_age_n <- 
  grp_analysis(nationals, y = "take_vaccine_num", x = "age_groups_three") %>%
  dplyr::filter(statistic != Inf) %>%
  dplyr::filter(conf.low > 0)

ans_n <- 
  dplyr::bind_rows(
    main_results_n %>% mutate(cat = "All", var = "All"),
    acc_by_gender_n %>% rename(cat = gender) %>% mutate(var = "By gender"),
    acc_by_educ_binary_n %>% rename(cat = educ_binary) %>% mutate(var = "By education"),
    acc_by_age_n %>% rename(cat = age_groups_three) %>% mutate(var = "By age")) %>%
  dplyr::mutate(across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 1))) %>%
  filter(group == "All") %>%
  mutate(group = "All LMICs (National samples)",
         tag = "All LMICs (National samples)")

@@

ans_national <- 
  ans_n %>% 
  dplyr::filter(group == "All LMICs (National samples)" & cat == "All")

@@

fig_hist_loo <- 
  loo_estimates %>%
  dplyr::mutate(estimate = estimate*100) %>% 
  ggplot(aes(estimate, color = tag, fill = tag)) + 
  geom_histogram(aes(y = ..density..), bins = 200, 
                 position = "dodge", alpha = .3, size = .3) +
  geom_vline(data = ans_loo, 
             aes(xintercept = estimate, color = cat, linetype = group), size = .9) +
  facet_grid_paginate(var + tag ~ m)  +
  scale_color_manual(
    name = "Subgroups", 
    values = safe_colorblind_palette) + 
  scale_fill_manual(
    name = "Subgroups", 
    values = safe_colorblind_palette) + 
  scale_linetype_manual(
    name = "Sample Average", 
    values = c("solid", "11", "dashed")) + 
  scale_x_continuous(n.breaks = 8, name = "estimate") +
  scale_y_continuous(
    labels = scales::percent_format(scale = 1, suffix = "", accuracy = 0.1)) +
  labs(title = "",
       x = "") +
  guides(color = guide_legend(reverse = TRUE, nrow = 2, keyheight = 1),
         fill = guide_legend(reverse = TRUE, nrow = 2, keyheight = 1),
         linetype = guide_legend(keyheight = 2)) +
  theme_bw(base_size = (base_font_size - 2)) +
  theme(legend.position = "bottom")

fig_hist_loo

@@

all_tables_n <- 
  main_table_n %>% 
  dplyr::left_join(gender_table_n) %>%
  dplyr::left_join(educ_table_n) %>% 
  dplyr::left_join(age_table_n) %>%
  dplyr::filter(group == "All") %>%
  dplyr::mutate(group = "All LMICs (National)")

@@

#Table to Latex
tab_reasons_y <- 
  yes_vacc2 %>%
  knitr::kable(
    col.names = cnames,
    caption = "Reasons to take the vaccine", format = "latex", booktabs = T, 
    linesep = "", label = "yes", 
    format.args = list(big.mark = ",", scientific = FALSE), 
    escape = F, align = "lcccc") %>%
  kableExtra::kable_styling(full_width = FALSE, 
                            font_size = base_font_size - 2) %>%
  kableExtra::add_header_above(c(" " = 2, "Protection" = 3), bold = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>% 
  kableExtra::column_spec(2:4, width = "4em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table S2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine. The number of observations and percentage corresponds only to people who would take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses. Studies India, Pakistan 1 and Pakistan 2 are not included because they either did not include the question or were not properly harmonized with the other studies.",
    threeparttable = T)

yes_vacc2 %>%
  knitr::kable(
    col.names = cnames,
    caption = "\\label{yes}Reasons to take the vaccine", 
    booktabs = T, linesep = "", 
    format.args = list(big.mark = ",", scientific = FALSE),
    align = "lcccc") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::add_header_above(c(" " = 2, "Protection" = 3), bold = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>% 
  kableExtra::column_spec(2:5, width = "8em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table S2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine. The number of observations and percentage correponds only to people who would take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses. Studies India, Pakistan 1 and Pakistan 2 are not included because they either did not include the question or were not properly harmonized with the other studies.",
    threeparttable = T)

@@

## Generate data for analysis of yes reasons for different age groups
yes_vacc_age_1 <- 
  lapply(yes_vars, age_analysis, df = df2, num = "Yes", filter_by = `age_less24`) %>%
  dplyr::bind_rows() %>%
  mutate(age = "<25")

yes_vacc_age_2 <- 
  lapply(yes_vars, age_analysis, df = df2, num = "Yes", filter_by = `age_25_54`) %>%
  dplyr::bind_rows() %>%
  mutate(age = "25-54")

yes_vacc_age_3 <- 
  lapply(yes_vars, age_analysis, df = df2, num = "Yes", filter_by = `age_55_more`) %>%
  dplyr::bind_rows() %>%
  mutate(age = "55+")

#Get percentage per yes reason category and make wide table
yes_vacc_age <- 
  rbind(yes_vacc_age_1, yes_vacc_age_2, yes_vacc_age_3) %>%
  dplyr::mutate(across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 0))) %>%
  dplyr::mutate(estimate = format(estimate, nsmall = 0),
                conf_int = paste0("(", conf.low, 
                                  ", ", conf.high, ")"),
                n = as.character(n)) %>%
  dplyr::select(group, estimate, conf_int, outcome, age, n) %>%
  tidyr::pivot_wider(names_from = c(outcome, age), values_from = c(estimate, conf_int, n), names_sep = "__") %>%
  tidyr::pivot_longer(cols = c(starts_with("estimate__"), starts_with("conf_int__"), starts_with("n__")),
                      names_to = c("type", ".value"),
                      names_pattern = "(.*)__(.*)")

y1 <- yes_vacc_age %>%
  dplyr::filter(grepl("yes_vaccine_1", type)) %>%
  dplyr::mutate(type = ifelse(grepl("estimate", type), "estimate", type),
         type = ifelse(grepl("conf_int", type), "conf_int", type),
         type = ifelse(grepl("n__", type), "n", type))

y2 <- yes_vacc_age %>%
  dplyr::filter(grepl("yes_vaccine_2", type)) %>%
  dplyr::mutate(type = ifelse(grepl("estimate", type), "estimate", type),
         type = ifelse(grepl("conf_int", type), "conf_int", type),
         type = ifelse(grepl("n__", type), "n", type))

y3 <- yes_vacc_age %>%
  dplyr::filter(grepl("yes_vaccine_3", type)) %>%
  dplyr::mutate(type = ifelse(grepl("estimate", type), "estimate", type),
         type = ifelse(grepl("conf_int", type), "conf_int", type),
         type = ifelse(grepl("n__", type), "n", type))

yes_vacc_age <- 
  dplyr::left_join(y1, y2, by = c("group", "type")) %>%
  dplyr::left_join(y3, by = c("group", "type")) %>% 
  dplyr::mutate(
    group = forcats::fct_relevel(as.factor(group), "All", "Russia", "USA", after = Inf)) %>% 
  dplyr::arrange(group) %>% 
  dplyr::mutate(
    across(c(group), 
           ~ifelse(type == "conf_int", "Conf. interval", as.character(.))),
    across(c(group), ~ifelse(type == "n", "n", as.character(.))),
    group = ifelse(group == "All", "All LMICs", group)) %>% 
  dplyr::select(-type)

@@

#Table to Latex
tab_reasons_y_age <- 
  yes_vacc_age %>%
  knitr::kable(
    col.names = cnames,
    caption = "Reasons to take the vaccine- by age groups", 
    format = "latex", booktabs = T, 
    linesep = "", label = "yes1", 
    format.args = list(big.mark = ",", scientific = FALSE), 
    escape = F, align = c("l", rep("c", 9))) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
                            font_size = base_font_size - 2, full_width = FALSE) %>%
  kableExtra::add_header_above(c(" " = 1, "Self" = 3, "Family" = 3, "Community" = 3), 
                               bold = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::row_spec(seq(from = 3, to = 36, by = 3), hline_after = TRUE) %>%
  kableExtra::column_spec(1, width = "7em") %>% 
  kableExtra::column_spec(2:10, width = "5em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table S4 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine by age groups. The number of observations and percentage correponds only to people who would take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses.",
    threeparttable = T)

yes_vacc_age %>%
  knitr::kable(
    col.names = cnames,
    caption = "\\label{yes1}Reasons to take the vaccine", 
    booktabs = T, linesep = "", 
    format.args = list(big.mark = ",", scientific = FALSE),
    align = c("l", rep("c", 9))) %>% 
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::add_header_above(c(" " = 1, "Self" = 3, "Family" = 3, "Community" = 3), 
                               bold = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>% 
  kableExtra::column_spec(2:10, width = "4em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table S4 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine by age groups. The number of observations and percentage correponds only to people who would take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses.",
    threeparttable = T)

@@

fig_2

@@

no_vacc2 %>%
  knitr::kable(
    col.names = c("Study", "N", 
                  "Concerned about side effects", 
                  "Concerned about getting coronavirus from the vaccine", 
                  "Not concerned about getting seriously ill", 
                  "Doesn't think vaccines are effective", 
                  "Doesn't think Coronavirus outbreak is as serious as people say", 
                  "Doesn't like needles", 
                  "Allergic to vaccines", 
                  "Won't have time to get vaccinated", 
                  "Mentions a conspiracy theory", 
                  "Other reasons"),
    caption = "\\label{no}Reasons not to take the vaccine", 
    booktabs = T, linesep = "", 
    format.args = list(big.mark = ",",scientific = FALSE),
    align = c("l", rep("c", 11))) %>%
  kableExtra::kable_styling(full_width = F) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1:12, width = "7em") %>%
  # kableExtra::column_spec(1, width = "7em") %>%
  kableExtra::footnote(
    general_title = "",
    general = "Table S5 shows percentage of respondents mentioning reasons why they would not take the Covid-19 vaccine. The number of observations and percentage correponds only to people who would NOT take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses.",
    threeparttable = T)

@@

trust <- filter(trust_vacc_together, sub == "Any")

@@

trust_all <- 
  trust %>% 
  dplyr::filter(group == "All" & tag == "Health workers") %>%
  dplyr::arrange(desc(estimate))

@@

fig_hist_categories
